%-------------------------
% Resume in LaTeX
% Author : Francis Paul Amadeo
% Based off of: https://www.overleaf.com/project/65a471c32f9ee1db3a96cc75
%------------------------

\documentclass[11pt,letterpaper]{article}
% \documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
% \usepackage[top=0.4in,bottom=0.4in,left=0.5in,right=0.5in]{geometry}
% Select font (comment out lines 6-9 to use Computer Modern)
%\usepackage{charter}
% \usepackage[default]{lato}
% \usepackage[sfdefault]{carlito}
 \usepackage{tgpagella}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{comment}
\raggedright
\pagestyle{empty}
\input{glyphtounicode}
\pdfgentounicode=1


%-------------------------
% Custom commands
% format section headings
\titleformat{\section}{\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-8pt}]

% format bullet points
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt}
%-------------------------------------------

% format subheadings
% {Title}{suplement text}{date/s}
% OUTPUT:|#1_#2___________#3|
\newcommand{\subheading}[3]{
    \textbf{#1}{ #2 }{\hfill #3 \vspace{-2pt}}
}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\centerline{\Huge Francis Paul Amadeo}
\centerline{francispaul.dev@gmail.com | linkedin.com/in/franpaul/}
% --\centerline{francispaul.dev@gmail.com | francispaul.dev}

%-----------EXPERIENCE-----------------

\section*{EXPERIENCE}
\subheading{Software Developer}{ Epic Systems -- Verona, WI}{Feb 2020 -- June 2023 \\}
\vspace{-5pt}
\begin{itemize}
  \item Decreased the review process for training to be billed from 4 weeks to 2 weeks by automating multiple manual steps. This also allowed the accounting team to rotate half of the team to other tasks
  \item Redesigned the go-live scheduling tool with C\#, .NET, and Preact to include the majority of the tasks admins need to complete on a single page, all while preserving workflow and security guardrails.
  \item Streamlined admins' communications with trainees by redesigning Epic's e-learning hosting site with MSSQL, C\#, and .NET Core to be SCORM-compliant, allowing admins to monitor trainee progress.
  \item As the technical point person for Training Billing Tools, reviewed designs, analyzed functionalities and cross-dependencies, and developed and maintained tools, reports, and databases for stakeholders.
  \item Completed software development life cycle for projects as lead designer and lead developer.
  \item Translated technical concepts, information, and workflows into terms and proofs of concept that all parties could easily understand.
        %\item Coordinated deployments of new software, feature updates, and fixes.
        %\item Met with SMEs, stakeholders and developers regularly to ensure project requirements and timelines are met by reducing technical complexity without sacrificing functionality to the software.
        %\item Developed conversion and system implementation plans.
        %\item Went on rotational support for the EpicU application.

\end{itemize}
\vspace{-5pt}
\subheading{Computer Engineering Intern}{UIC College of Engineering -- Chicago, IL}{ July 2019 -- Aug 2019 \\}
\vspace{-5pt}
\begin{itemize}
  \item Designed and implemented the python-based circuit simulator used for UIC's first offering of ECE 464 (Testing and Reliability of Digital Systems)
  \item Provided detailed documentation to allow students to clearly understand the program.
\end{itemize}
\vspace{-5pt}
\begin{comment}
\subheading{Engineering Student Ambassador/Mentor}{UIC College of Engineering}{July 2019 -- Aug 2019 \\}
\vspace{-5pt}
\begin{itemize}
  \item Taught review classes and workshops on Math, Physics, Chemistry, Robotics, Circuits,among others, for 18 incoming freshmen.
  \item Guided my personal mentee’s success and first year experience at the University
\end{itemize}
\vspace{-10pt}
\end{comment}
%-----------PROJECTS-----------------
\section{PROJECTS}
\subheading{Project Stella}{}{}
%engineering.uic.edu/news-stories/strong-showing-by-edt-robots-at-engineering-competition/ \\
\vspace{-5pt}
\begin{itemize}
  \item Won 2nd place in the Midwestern Robotics Design Competition 2019 at UIUC.
  \item As the Software Lead,  oversaw and delegated various electrical and programming duties among the electrical and CS team.
\end{itemize}
\vspace{-5pt}
\subheading{Print-a-Part}{}{}
\vspace{-5pt}
\begin{itemize}
  \item  As Outreach Director, Initiated and oversaw the relaunch of Chicago EDT's outreach program, Print-a-Part, where students can submit their 3D CAD designs and get them printed and sent for free.
\end{itemize}
\vspace{-10pt}
\begin{comment}
\{}{}{NASA Robot Mining Competition}{-- Team Lunabotics} \\
\vspace{-5pt}
\begin{itemize}
  \item  Initiated and oversaw the conversion of Chicago EDT's  existing assets from Altium Designer to Autodesk EAGLE \\
\end{itemize}
\vspace{-10pt}
\end{comment}
%
%--------SKILLS------------
\vspace{-5pt}
\section*{SKILLS}
\textbf{Languages:} C, C++, C\#, HTML, Javascript, Typescript, Python, MSSQL, LaTeX, VHDL, Assembly \\
\textbf{Frameworks:} .NET,.NET Core, Angular, React.js \\
\textbf{Version Control:} Git, SVN \\
\textbf{Standards:} ARIA, SCORM \\
%\textbf{Tools:} Visual Studio,Visual Studio Code,KDiff3,Visio,   \\
%\textbf{Spoken Languages:} Filipino
%\textbf{Other:} Arduino, AutoCAD, PCB Design, Simulink,Roboteq, Chronicles \\
%-------------------------------------------

%-----------EDUCATION-----------------
\section*{EDUCATION}
\subheading{University of Illinois at Chicago}{-- Bachelor of Science in Computer Engineering}{2019} \\
\vspace{-8pt}
\begin{itemize}
  \item Graduated \textit{cum laude}
  \item IEEE-Eta Kappa Nu Honor Society Member \\ %etakappanu.students.uic.edu
  \item Tau Sigma National Honor Society Member
\end{itemize}
\vspace{-5pt}
\subheading{College of Lake County}{-- Associate Degree in Engineering Science}{2017 } \\
\vspace{-8pt}
\begin{itemize}
  \item Graduated with High Honors
  \item Honoree of Certification of Academic Distinction
  \item Phi Theta Kappa National Honor Society Member
\end{itemize}
\vspace{-10pt}
%-------------------------------------------
\end{document}
